\section*{WU6}
We got the best result afert 81 training iterations.
Training accuracy 0.54, test accuracy 0.62


The top and bottom five had weights with the same values so we extended the list from 5 to 7 for the positiv values.
We did the same thing for the negative ones where we extended the list from 5 to 6.

Below you can see the top and bottom weights and their corresponding classes.


\begin{verbatim}
computer processing of pictorial information
9.0
advanced computer graphics
8.0
database management systems
7.0
computational methods
5.0
computer networks
5.0
data structures
5.0
introduction to information technology
5.0


honors seminar
-8.0
introduction to c programming
-6.0
program analysis and understanding
-5.0
object-oriented programming i
-5.0
object-oriented programming ii
-4.0
computer networks
-4.0
\end{verbatim}
There were two things that were interesting in these weights:
\begin{itemize}
 \item the top two positiv weights are both advanced computer graphics courses. Which makes sense because they require the student to take the lower level
 computer graphics course that we are looking for.
 \item no course from AI area had a high or low weight associated with it. Which might explain the bad test results. For good results you would expect an AI class to show up in the positiv or negativ weights.
\end{itemize}

Besides that there seemed to be no logical reason for choosing these classes that we could think of.

Why is it hard to interpret "large weight" as "most indicative"?:
       The perceptron is looking for patterns in the training data but it might find patterns that are not really meaningful for prediction. E.g. most of
       the     negativ weights are introductory classes which doesn't really make sense when you want to predict if someone took a certain class because
       everyone takes these classes.

Comparison with Decision Tree:
       Except for "program analysis and understanding" which is a question in the decision tree and a high negativ weight in the perceptron, there are
       no other items that are overlapping.